---
title: "Tidyverse Assignment - Purrr and Forcats and Vignette"
author: "Cameron Smith"
date: "10/26/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Introduction

This vignette is focused on the purrr and forcats packages from the Tidyverse, and were chosen based on the simple logic that I am the least unfamiliar with them so it seemed like a good opportunity to change that.

### Load packages

Loading the two packages directly, though you could also load the whole tidyverse package

```{r}
library(purrr)
library(forcats)
library(dplyr)
```

### Load the data

I used a dataset from Kaggle with information on Indian cuisine (link and info below.  It is stored in Github for reproducibility.

https://www.kaggle.com/nehaprabhavalkar/indian-food-101
Version 2, Accessed 26 October 2020

```{r}
file <- "https://raw.githubusercontent.com/cwestsmith/cuny-msds/master/datasets/indian_food.csv"
df <- read.csv(file, header = TRUE)
# Checking structure of new data frame.  Lots of factors, which is good for this vignette
str(df)
```

### Example 1: Forcats

Forcats is focused on making it easier to work with factors in R.  One such function is fct_infreq(), which reorders a factor based on the frequency of values it has.  In the example below I will use this function to reorder the flavor_profile variable based on the frequency of its levels in the dataset.

```{r}
# View current structure of flavor_profile factor
levels(df$flavor_profile)

# View summary of each flavor_profile based on # of entries
df %>% group_by(flavor_profile) %>% summarise(n())

# Re-order the flavor_profile
df$flavor_profile <- fct_infreq(df$flavor_profile)

# Now view it again, which should match the order per the summary above
levels(df$flavor_profile)
```

### Example 2: purrr

Purr is focused on making it easier to work with functions and vectors in R.  One such function is pluck() which provides a flexible way to quickly extract an element.  It has a sister function named chuck() which is similar except that it throws errors when something does not exist, rather than simply returning NULL.

```{r}

# Create an example list
example_list <- as.list(df$ingredients)

# Pluck an element by index
pluck(example_list, 1)

# Searching for element that does not exist - pluck returns NULL
pluck(example_list, 100000)

# But chuck returns an error
chuck(example_list, 100000)
```

### Conclusion

In conclusion Forcats and Purr both include a wide array of useful functions which make it easier to work with various types of data in R.