---
title: "Tidyverse with Groceries Data"
author: "DH Kim"
output:
  rmarkdown::html_vignette:
vignette: >
  %\VignetteIndexEntry{Tidyverse with Groceries Data}  
  %\VignetteEngine{knitr::rmarkdown} 
  %\usepackage[utf8]{inputenc}
---

This document shows some data work with the `readr`, `dplyr`, `stringr`, and `ggplot2` libraries in tidyverse, focusing on how to use functions. The dataset used comes from [Kaggle Groceries dataset](https://www.kaggle.com/heeraldedhia/groceries-dataset). 

```{r load-packages, message=FALSE}
# libraries in Tidyverse
library(readr)
library(dplyr)
library(stringr)
library(ggplot2)
```

### Importing data with readr::read_*()

It shows how to use the `read_csv()` function in the readr library and its, which is different from the built-in `read.csv()` function. The R documentation for read_csv() is [here](https://readr.tidyverse.org/reference/read_delim.html) and the one for read.csv() is [here](https://www.rdocumentation.org/packages/utils/versions/3.6.2/topics/read.table).
```{r code-chunk-label}
groceries <- 
  read_csv(url("https://raw.githubusercontent.com/HwanKim2/data_repo/main/Groceries_dataset.csv"))
glimpse(groceries)
```

The resulting data frame is *groceries*. Some variants are as follows. The first one explicitly writes down the default options in the function.
```{r}
gro_varOne <- readr::read_csv(
  url("https://raw.githubusercontent.com/HwanKim2/data_repo/main/Groceries_dataset.csv"),
  col_names = TRUE, col_types = NULL)
glimpse(gro_varOne)
identical(groceries, gro_varOne)
```

It shows how to explicitly specify the `col_types` option.
```{r}
gro_wayTwo <- 
  read_csv(
    url("https://raw.githubusercontent.com/HwanKim2/data_repo/main/Groceries_dataset.csv"),
       col_types = cols(
                   Member_number = col_double(),
                   Date = col_character(),
                   itemDescription = col_character()
                   )
          )
identical(groceries, gro_wayTwo)
```
For more, you may refer to [other read_csv() vignette](https://github.com/palmorezm/FALL2020TIDYVERSE/blob/Zach_Vignette/Tidyverse_Vignette.Rmd).

### Counting observations by group with count()

```{r}
item_count <- groceries %>%
  dplyr::count(itemDescription) %>%
  arrange(desc(n))
item_count[1:10,]
```
The above data work is simplified with the sort option.
```{r}
item_count_varOne <- groceries %>%
  dplyr::count(itemDescription, sort = TRUE)
item_count_varOne[1:10,]
identical(item_count, item_count_varOne)
```

### Plotting with ggplot()
```{r}
ggplot(item_count[1:10,], 
       aes(x=reorder(itemDescription, -n), y = n)) +
geom_bar(stat="identity") +
labs(x = "", y = "quantity sold") +
theme(axis.text.x = element_text(angle = 45, vjust = 0.5, hjust=1))
```

&nbsp;

&nbsp;

&nbsp;

