---
title: "TidyVerse Assignment"
author: "John Mazon"
date: "10/25/2020"
output: html_document
---
### Loading the librarys

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
##library(tidyverse) - will load the core tidyverse packages
## can be loaded seperate
#Similarly to readr , dplyr and tidyr are also part of the tidyverse. These packages were loaded in R's memory when we called library(tidyverse)

library(readr)
#for data import

library(ggplot2)
#for data visualisation

library(dplyr)
#for data manipulation

library(tidyr)
#for data tidying

library(tibble)
#for tibbles, a modern re-imagining of data frames
```

## Task at Hand
In this assignment, you’ll practice collaborating around a code project with GitHub.  You could consider our collective work as building out a book of examples on how to use TidyVerse functions.
Your task here is to Create an Example.  Using one or more TidyVerse packages, and any dataset from fivethirtyeight.com or Kaggle, create a programming sample “vignette” that demonstrates how to use one or more of the capabilities of the selected TidyVerse package with your selected dataset. 

Additionally, we will internally work for the purpose of demonstration to 
and show a graphic of correlation between clarity variable and depth variable


## Data Sources and Background
Dataset found in Kaggle site:
This dataset contains the prices and various attributes of almost 54,000 diamonds. Specifically, it is a data frame with 53940 rows and 10 variables. Some characteristics specified for each row are price[in U.S Dollars], carat, cut quality, color, clarity, total depth percentage and table.  

https://www.kaggle.com/shivam2503/diamonds


GitHub repository to be utilized: 
https://github.com/acatlin/FALL2020TIDYVERSE


# Vignette

## Functionality #1 - Reading in the data using readr

Although standard R has the ability to load csv files, using the read.csv() function, we’ll use the functions in the readr Tidyverse package to load this data.

```{r}
#use read_csv function from readr to import csv file
diamond_data <- read_csv("https://raw.githubusercontent.com/johnm1990/DATA607/master/diamonds.csv")
#as_tibble() turns an existing object, such as a data frame or matrix, into a so-called tibble, a data frame with class tbl_df . 
diamond_data <- as_tibble(diamond_data)
head(diamond_data)

```

## Functionality #2 - slice

'slice()' lets you index rows by their (integer) locations. It allows you to select, remove, and duplicate rows. It is accompanied by a number of helpers for common use cases
```{r}
#
slice(diamond_data, 1:8)


#select the first or last rows.
slice_head(diamond_data)
slice_tail(diamond_data)

#randomly selects rows
slice_sample(diamond_data)

```

## Functionality #3 - mutate
mutate() adds new variables and preserves existing ones; 

Here using we could depict a ratio of price to depth and include the result in a new column 'Ratio'
```{r}

diamond_data %>% select(price, depth) %>% mutate(Ratio = price/depth)


```


## Functionality #4 - select
select() is used to take a subset of a data frame by columns.
Below we use this function to take a subset of only included values clarity and depth. The rest of the uneeded variables con be removed
```{r}
diamond_data <- select(diamond_data, -X1, -z, -color, -cut, -carat, -price)

diamond_data

```


## Functionality #5 - Visualization - ggplot
The point geom is used to create scatterplots. The scatterplot is most useful for displaying the relationship between two continuous variables.
Below we use this function to see the amount correlation between clarity variable and depth variable

```{r}

# Basic barplot
ggplot(diamond_data) +
  geom_point(aes(clarity, depth))
  
   

```


